---
title: "hw_8"
author: "Holden Mitchell"
date: "10/28/2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework 8

Assignment
8-1, 8-9, 8-23, 8-34 (R codes required if available)
9-1, 9-2, 9-8, 9-18, 9-20, 9-21, 9-23, 9-25, 9-28, 9-38, 9-39, 9-40 (R codes required if available)

#### 8-1

a. The numbers suggest some firms gained while others stayed the same.

b. H<sub>0</sub>: u<sub>d</sub> \(\leq \) 0
  H<sub>1</sub>: u<sub>d</sub> > 0
  
```{r}
data = data.frame("firm" = c(seq(1:12)),
                  "b" = c(5,7,1,2,4,3,2,7,1,2,7,5),
                  "a" = c(8,9,3,2,4,3,8,7,5,3,4,6))
data$difference = data$a - data$b

u = mean(data$difference)
sd = sd(data$difference)
n = 12

t.test(data$a, data$b, alternative = "greater", mu = 0, paired = TRUE)
```

c. populations are normal, time is not a factor, same firms are involved in both samples, other factors have not changed.

d. One tail, \(\alpha \) = 0.05
e. t = 2  
0.0354

#### 8-9

```{r}
n1 = 128
n2 = 212
u1 = 23.5
u2 = 18
sd1 = 12.2
sd2 = 10.5


z = (u1 - u2 - 0)/sqrt((sd1^2/n1)+(sd2^2/n2))

p_value = 2*pnorm(-abs(z))
p_value
```

z = 4.24
Reject H<sub>0</sub>

#### 8-23

```{r}
n1 = 25
n2 = 25
u1 = 12
u2 = 13.5
sd1 = 2.5
sd2 = 1

z = (u1 - u2 - 0)/sqrt((sd1^2/n1)+(sd2^2/n2))

pnorm(-abs(z))
```

t = 2.785, reject H<sub>0</sub> at both \(\alpha \)

#### 8-34

32% credit safer
19% debit safer

n = 100
0.01 significance

```{r}
n1 = 100
n2 = 100
p1 = .32
p2 = .19

z = (p1 - p2 - 0)/sqrt(((p1*(1-p1))/n1)+((p2*(1-p2))/n2))

p_value = 2*pnorm(-abs(z))
p_value
```

#### 9-1

Series of paired t-test are dependent on each other, therefore there is no control over the probability of a Type I error

#### 9-2

5 plants
df<sub>n</sub> = 5 - 1 = 4
df<sub>d</sub> = 21 - 5 = 16

```{r}
n = 4
d = 16
f = 2.33

1 - pf(f, n, d)
```


#### 9-8

US: n = 200
France: n = 150
China: n = 171

* a. H<sub>0</sub>: All 3 are equally effective
* H<sub>1</sub>: Not all 3 are equally effective
* b. The factor is the different countries
* c. 199 + 149 + 170 = 518
* d. 2
* e. 518 + 2 = 520

#### 9-18


a. H<sub>0</sub>: \(\mu \)<sub>stocks</sub> = \(\mu \)<sub>value</sub> = \(\mu \)<sub>past</sub> 
H<sub>1</sub>: \(\mu \)<sub>stocks</sub> \(\neq \) \(\mu \)<sub>value</sub> \(\neq \) \(\mu \)<sub>past</sub>
b. 3815 
c. 2 
d. 3817
e. The f-value is 4.61 with a p-value of 0.01000732

#### 9-20

H<sub>0</sub>: \(\mu \)<sub>a</sub> = \(\mu \)<sub>b</sub> = \(\mu \)<sub>c</sub>
H<sub>1</sub>: \(\mu \)<sub>a</sub> \(\neq \) \(\mu \)<sub>b</sub> \(\neq \) \(\mu \)<sub>c</sub>

```{r}
valueA = c(4420,4540,4380,4550,4210,4330,4400,4340,4390,4510)
valueB = c(4230,4220,4100,4300,4420,4110,4230,4280,4090,4320)
valueC = c(4110,4090,4070,4160,4230,4120,4000,4200,4150,4220)


data = data.frame("value" = c(valueA, valueB, valueC),
                  "group" = c(rep("A", 10), rep("B", 10), rep("C", 10)))

this =aov(value ~ group, data = data)
summary(this)

```

Reject the null; p-value is close to 0

#### 9-21

H<sub>0</sub>: u<sub>UK</sub> = u<sub>Mexico</sub> = u<sub>UAE</sub> = u<sub>Oman</sub> 
H<sub>1</sub>: u<sub>UK</sub> \(\neq \) u<sub>Mexico</sub> \(\neq \) <sub>UAE</sub> \(\neq \) <sub>Oman</sub>

```{r}
price_uk = c(62.10, 63.2, 55.8, 56.9, 61.2, 60.18, 60.9, 61.12)
price_mex = c(56.3,59.45,60.02,60.00,58.75,59.13,53.30,60.17)
price_uae = c(55.6,54.22,53.18,56.12,60.01,53.20,54,55.19)
price_oman = c(53.11,52.9,53.75,54.1,59.03,52.35,52.8,54.95)

data = data.frame("price" = c(price_uk, price_mex, price_uae, price_oman), "country" = c(rep("uk", 8), rep("mex", 8), rep("uae", 8), rep("oman", 8)))

this =aov(price ~ country, data = data)
summary(this)
```

p-value = 0, Reject H<sub>0</sub>

#### 9-23

H<sub>0</sub>: u<sub>high</sub> = u<sub>medium</sub> = u<sub>low</sub>
H<sub>1</sub>: u<sub>high</sub> \(\neq \) u<sub>medium</sub> \(\neq \) u<sub>low</sub> 

```{r}
months_h = c(3.5,4.8,3.0,6.5,7.5,8,2,6,5.5,6.5,7,9,5,10,6)
months_m = c(3,5.5,6,4,4,4.5,6,2,9,4.5,5,2.5,7)
months_l = c(1,2.5,2,1.5,1.5,6,3.8,4.5,0.5,2,3.5,1,2)

data = data.frame("months" = c(months_h, months_m, months_l), "speed" = c(rep("high", 15), rep("medium", 13), rep("low", 13)))

this =aov(months ~ speed, data = data)
summary(this)
```

p-value = 0, Reject H<sub>0</sub>

#### 9-25

```{r}
price_uk = c(62.10, 63.2, 55.8, 56.9, 61.2, 60.18, 60.9, 61.12)
price_mex = c(56.3,59.45,60.02,60.00,58.75,59.13,53.30,60.17)
price_uae = c(55.6,54.22,53.18,56.12,60.01,53.20,54,55.19)
price_oman = c(53.11,52.9,53.75,54.1,59.03,52.35,52.8,54.95)

data = data.frame("price" = c(price_uk, price_mex, price_uae, price_oman), "country" = c(rep("uk", 8), rep("mex", 8), rep("uae", 8), rep("oman", 8)))

mse = 62.89
n = length(data$price)
q = 2.92
turkey = q*sqrt(mse)/sqrt(n)
turkey
```

UK - UAE
UK - OMAN
MEX - OMAN

#### 9-28

F(1,180) = 4.12
p < .05

a. 1, yes 
b. 181 * 4 = 724
c. Not significant
d. No because the p-value is right on the border of being significant or not.
```{r}
1 - pf(4.12, 1,180)
```
e. 0.0438
#### 9-38


```{r}
salaries_east = c(54,61,59,56,70,62,63,57,68,48,50,49,60,54,52,49,55,53,71,76,65,70,68,62,73,60,79)
salaries_central = c(52,50,58,59,62,57,58,64,61,44,49,54,53,51,60,55,47,50,61,64,69,58,57,63,65,63,50)
salaries_west = c(63,67,68,72,68,75,62,65,70,65,58,62,70,57,61,68,65,73,82,75,79,77,80,69,84,83,76)

data = data.frame("salaries" = c(salaries_east, salaries_central, salaries_west), "location" = c(rep("east", 27), rep("central", 27), rep("west", 27)), "job" = c(rep("type1", 9), rep("type2", 9), rep("type3", 9), rep("type1", 9), rep("type2", 9), rep("type3", 9),rep("type1", 9), rep("type2", 9), rep("type3", 9)))

this <- aov(salaries ~ location + job, data = data)
summary(this)
```

#### 9-39

a. Explained is treatment. Explained = Factor A + Factor B + (AB)
b. 3
c. 2
d. 150
e. 25
f. No, there are no exercise price main effects
g. Yes, there are time-of-expiration main effects at 0.05, but not at 0.01
h. No interactions
i. There is no evidence for exercise-price main effects or interaction effects. However, the is some evidence for time-of-expiration main effects.


```{r}
f_exercise = .420
f_time = 4.845
f_interaction = 0.193
n = 150
d_exercise = 2
d_time = 1
d_interaction = 2
1 - pf(f_exercise,d_exercise,n)
1 - pf(f_time,d_time,n)
1 - pf(f_interaction, d_interaction,n)
```
j. Only Time is significant

k. T-test


#### 9-40

a. 2
b. 2
c. No, there are no significant task difficulty main effects
d. Yes, there are significant effort main effects
e. No interactions, p-value is greater than 0.05.