---
title: "hw_4_group"
author: "Holden Mitchell"
date: "9/25/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
customer = c(1,2,3,4)
quantity = c(12, 8, 5, 2)
price = c(57810, 8640540, 97800, 4015000)
exchange_mean = c(1.41, 0.00904, 0.824, 0.0211)
exchange_sd = c(0.041, 0.00045, 0.0342, 0.00083)
data = data.frame(customer = customer, quantity = quantity, price = price, exchange_mean = exchange_mean, exchange_sd = exchange_sd)
data
```

1. Mean, Variance, and Standard Deviation in US $

```{r}
data$us_dollars = data$price * data$exchange_mean
data$us_sd = data$price * data$exchange_sd
data$revenue = data$quantity * data$us_dollars
data$revenue_sd = data$quantity * data$us_sd
mean = sum(data$revenue)
sd = sum(data$revenue_sd)
var = sum(data$revenue_sd)^2
mean
```

Mean: 2175398
Variance: 6878573172
Standard Deviation: 82937.16

2.

```{r}
pnorm(2250000, mean = mean, sd = sd, lower.tail = FALSE)
```

3.

```{r}
pnorm(2150000, mean = mean, sd = sd)
```
4. 

```{r}
pnorm(2150000, mean = mean, sd = sd, lower.tail = FALSE)
```
* There is a 62% chance that we will exceed that revenue.

5. 

* Based on the fact that the odds are favored towards us making more than the $2,150,000, I would suggest that we not take the offer.

6.

I would say the the sales manager is more risk-averse because though the odds are in the favor of beating that revenue, there is still a chance that the company could make less, while the buyout is a sure thing.

7.

```{r}
pnorm(2150000, mean = mean, sd = sd)
```

8.

```{r}
pnorm(2039000, mean = mean, sd = sd)

value_at_risk = 2150000 - 2039000
value_at_risk
```

9. 

```{r}
expected_profit = mean - 2150000
expected_profit
```


10.

```{r}
value_at_risk / expected_profit
```
Based on the bank's definition of value at risk and the expected profit, the bank is facing a high amount of risk with this deal.

11.

By converting the currencies, you open yourself up to more risk because of the possibility that the currencies decrease.

12.

No it is not.