---
title: "hw_9"
author: "Holden Mitchell"
date: "11/2/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chapter 10

10-15, 10-21, 10-39, 10-44, 10-51, 10-63, 64, 65, 66, 10-69, 70, 11-4 (Ch. 11)
Risk and Return (group)

#### 10-15

```{r}
inflation = c(1,2,12.6,-10.3,0.51,2.03,-1.8,5.79,5.87)
return = c(-3,36,12,-8,53,-2,18,32,24)

data = data.frame("inflation" = inflation, "return" = return)

linearMod = lm(return ~ inflation, data = data)
summary(linearMod)
anova1 <- aov(linearMod)
summary (anova1)
plot(linearMod)
```

* Yes there is a linear relationship
* 16.0961 + 0.9681x


#### 10-21

```{r}
x = c(27,39,73,66,33,43,47,55,60,68,70,75,82)
y = c(2,3,10,9,4,6,5,8,7,9,10,13,12)

data = data.frame("x" = x, "y" = y)

linearMod = lm(y ~ x, data = data)
summary(linearMod)
anova2 = anova(linearMod)
summary(anova2)

confint(linearMod,"x",level=0.95)
```


* [0.150, 0.222]
* Zero is not plausible

#### 10-39

P = Avg. Price per share
x_k = (X/k) contemporaneous earnings per share divided by firm-specific discount rate

H<sub>0</sub>: B<sub>1</sub> = 0
H<sub>1</sub>: B<sub>1</sub> \(\neq \) 0

```{r}
n = 213
b1 = 0.68
s_b1 = 12.03

t = b1 / s_b1
t
```

t = 0.0565, do not reject H<sub>0</sub>. Cannot determine linear relationship based on givens.

#### 10-44

Y = return on stocks
X = market value

```{r}
n = 4921
b1 = -0.0053
s_b1 = 0.0019
```

a. H<sub>0</sub>: B<sub>0</sub> = 1  H<sub>1</sub>: B<sub>0</sub> \(\neq \) 1
```{r}
b1 / s_b1
```
b. t = -2.789474
* Reject H<sub>0</sub>
c. -2.789474
d. yes
e. a negative or inverse relationship
f. The repatriation rate decreases as profitability increases
g. There is a inverse relationship between a company's profitability and the repatriation rate. The null hypothesis was rejected because it is a linear relationship.

#### 10-51

a. A smaple size is needed to determine significance
b. It is a positive, linear relationship
c. The model only explains 2.6% of the variation in call price
d. No, r^2 is too small to use this model

#### 10-63

a. Heteroscedasticity
b. No model inadequacy
c. Moel inadequacy, because the data shows a curve (not linear)

#### 10-64

a. No model inadequacy
b. Yes, it increases with time

#### 10-65

a. No serious inadequacy
b. Yes. A deviation is visable in the model.

#### 10-66

Produce residual plots for regression of problem 10-17. Is there any apparent model inadequency?
```{r}
quartile<-c(1,2,3,4,5)
growth<-c(17.3,23.6,40.2,45.8,56.8)
money<-data.frame(quartile,growth)
linRegression<-lm(growth~quartile, data=money)
rPlot<-resid(linRegression)
plot(rPlot)
```

* Seems to have no correlation.

#### 10-69

```{r}
miles = c(1211,1345,1422,1687,1849,2026,2133,2253,2400,2468,2699,2806,3082,3209,3466,3643,3852,4033,4267,4498,4533,4804,5090,5233,5439)
dollars = c(1802,2405,2005,2511,2332,2305,3016,3385,3090,3694,3371,3998,3555,4692,4244,5298,4801,5147,5738,6420,6059,6426,6321,7026,6964)
american=data.frame(miles, dollars)
attach(american)
express=lm(dollars~miles)
prediction_1 = predict(express,data.frame(miles=5000), interval="prediction",
                 level = 0.95)
prediction_1

prediction_2 = predict(express,data.frame(miles=4000), interval="prediction",
                 level = 0.95)
prediction_2
```

* The 4000 is lower for fit, lwr and upr

#### 10-70

99% prediction
income quartile = 5

```{r}
predict(linRegression, data.frame(quartile=5), interval = "prediction", level = 0.99)
```

* See R output above

#### 11-4

```{r}
value = c(345,238,452,422,328,375,660,466,290)
size = c(1650,1870,2230,1740,1900,2000,3200,1860,1230)
distance = c(3.5,0.5,1.5,4.5,1.8,0.1,3.4,3.0,1.0)
home = data.frame("value" = value, "size" = size, "distance" = distance)

multi = lm(value ~ size + distance)
summary(multi)
anov = anova(multi)
anov
```
* y-intercept = -9.7997
* -9.7997 + 0.1733 s + 31.094 d

## Risk and Return


```{r}
market<-c(16.02,12.17,11.48,17.62,20.01,14,13.22,17.79,15.46,8.09,11,18.52,14.05,8.79,11.6)
stock<-c(21.05,17.25,13.1,18.23,21.52,13.26,15.84,22.18,16.26,5.64,10.55,17.86,12.75,9.13,13.87)
data<-data.frame(market,stock)
attach(data)
reg<-lm(stock~market,data=data)
```
#### 1)

```{r}
reg
```

\(\beta \) = 1.167
* -1.091 + 1.167x

#### 2)

* The slope indicates that the stock is barely above the average risk.

#### 3)

```{r}
confint(reg, "market",level=0.95)
```
* See r output above. No, the risk could be below average because the 2.5% is at 0.7929

#### 4)

```{r}
predict(reg, data.frame(market=10), interval = "prediction")
```
* 10.57884

#### 5)

```{r}
plot(resid(reg))
```
* Appears to have no correlation

#### 6)

```{r}
plot(reg)
```

* Yes they appear to be normally distributed