---
title: "homework_7"
author: "Holden Mitchell"
date: "10/22/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework 7

7-1,2,3,4,5, 7-7, 7-16, 7-27, 7-53 (need R codes if available)
Make sure Power Curve works (need codes and graph) script in downloads
Practice Calculating Beta (pp. 246-248) (need PowerPoint slides to present in class)

##### 7-1

* H<sub>o</sub>: \(\mu \) <= $3.75
* H<sub>1</sub>: \(\mu \) > $3.75

##### 7-2

* H<sub>o</sub>: \(\mu \) <= 200 ppm 
* H<sub>1</sub>: \(\mu \) > 200 ppm

##### 7-3

* H<sub>o</sub>: p = 0.8
* H<sub>1</sub>: p \(\neq \) 0.8

##### 7-4

* H<sub>o</sub>: \(\mu \) >= $49160
* H<sub>1</sub>: \(\mu \) < $49160

##### 7-5

* H<sub>o</sub>: \(\mu \) <= 12
* H<sub>1</sub>: \(\mu \) > 12

##### 7-7

a. Null, there are no weapons
* H<sub>0</sub>: No weapons
* H<sub>1</sub>: Weapons
b. 
* Type I error: rejecting the null hypothesis and concluding there are weapons when there are no weapons.
* Type II error: Concluding that there are not weapons when there actually are weapons.
c. 
* Type II error would be more costly in terms of endangering lives because a passenger would have weapons. 
* Type I would just be an inconvenience for the passenger because they do not have weapons
d. I would recommend the largest value of \(\alpha \) possible.
e. If the sensitivity of the detectors is increased, then the probability of a Type I error would increase and the probability of the Type II error would decrease.
f. If \(\alpha \) is increased, then the sensitivity of the dectectors should also be increased.

##### 7-16



```{r}
france = 65
n = 100
average = 71
sd = 46
```

* H<sub>o</sub>: France = 65
* H<sub>1</sub>: France \(\neq \) 65

a. Using \(\alpha \) = 0.05, conduct the appropriate test (95% confidence test)

```{r}
t = (france - average) / (sd / sqrt(n))
t
pvalue = 2*pt(-abs(t),df=n-1)
pvalue
```

Fail to reject H<sub>o</sub>

b. Using \(\alpha \) = 0.01, conduct the appropriate test (99% confidence test)

Fail to reject H<sub>o</sub>

c. What assumptions are you making?

* I am assuming that the population is normal and I think that is a valid assumption.

d. State your conclusions in a complete sentence

* I fail to reject the null hypothesis based on the assumption that the population is normal.

##### 7-27

a. I would consider differences based on geography, culture, income, demographics, and others.
b. A single sample might not be large enough if it is broken down several times.
c. 
```{r}
u = 158.8
n = 5000
xbar = 178.9
sd = 55
t = (xbar - u) / (sd / sqrt(n))
t
pvalue = 2*pt(-abs(t),df=n-1)
pvalue
```

t = 25.8415, p-value= 0.000 Reject at both \(\alpha \)

d. 

```{r}
u = 25.5
n = 5000
xbar = 41.2
sd = 15.7
t = (xbar - u) / (sd / sqrt(n))
t
pvalue = 2*pt(-abs(t),df=n-1)
pvalue
```

t = 70.7107, Reject at both \(\alpha \)

e. 

```{r}
u = 4.5
n = 5000
xbar = 8.6
sd = 5.1
t = (xbar - u) / (sd / sqrt(n))
t
pvalue = 2*pt(-abs(t),df=n-1)
pvalue
```

t = 56.8458, Reject at both \(\alpha \)

f.

```{r}
u = 2.6
n = 5000
xbar = 1.1
sd = .9
t = (xbar - u) / (sd / sqrt(n))
t
pvalue = 2*pt(-abs(t),df=n-1)
pvalue
```

t = 117.8511, Reject at both \(\alpha \)

g. 

```{r}
u = 200000000
n = 25
xbar = 121000000
sd = 48000000
t = (xbar - u) / (sd / sqrt(n))
t
pvalue = 2*pt(-abs(t),df=n-1)
pvalue
```

t = -8.2292, Reject at both \(\alpha \)

##### 7-53

H<sub>o</sub>: u >= 50
H<sub>1</sub>: u < 50

```{r}
u = 50
n = 200
xbar = 44
sd = 28.2
t = (xbar - u) / (sd / sqrt(n))
t
pvalue = 2*pt(-abs(t),df=n-1)
pvalue
```

t = -3.009, Reject H<sub>o</sub>

b. Yes, I computed the t and p value