---
title: "hw_10"
author: "Holden Mitchell"
date: "11/8/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### 11-19

a. Assume n = 50.
Regression is: Return = 0.484 - 0.030 (Siz rnk) - 0.017 (Prc rnk)
b. R^2 = 0.13. 13% of the variation is due to the two independent vaiables.
c. Adj. R^2 is quite low; try regressing on size alone.

#### 11-26

#### 11-29

Len seems insignificant because of collinearity with M<sub>1</sub> or Price

#### 11-30

a.
b.
c.
d.
e.
f.


#### 11-31

profit = c(-1.2, -2.8, -0.2, 0.2)


b<sub>0</sub> = 834.95
b<sub>1</sub> = 0.0085
b<sub>2</sub> = -0.1741
R^2 = 0.3823
F = 2.166
Regression is not significant

#### 11-37

a. BV: t = 26.2 sig.
  Inc: t = 37.809 sig.
  Intercept: t = 0.2654 no sig.
b. p-value < 0.001 for both independent variables
c. Yes
d. 91% of variation explained

#### 11-46 

#### 11-47

An observation far from the others

#### 11-48

#### 11-50

#### 11-51

The estimators are the same although their standard errors are different

#### 11-52

#### 11-53

#### 11-57

Early investment is not statistically significant (or may be collinear with another variable). Rerun the regression without it. The dummy variables are both significant. Investment is significant.

#### 11-59

#### 11-63

a. IndAnalPersp is the only variable that is significant
b. p-value < 0.01
c. interactive second-order term
d. inverse relationship

#### Return on Capital for Four Different Sectors (Group)

```{r}

banks = c('Bank of New York', 'Bank United', 'Comerica', 'Compass Bancshares', 'Fifth Third Bancorp', 'First Tennessee National', 'Firstar', 'Golden State Bancorp', 'Golden West Financial', 'Greenpoint Financial', 'Hibernia', 'M&T Bank', 'Marshall & Ilsley', 'Northern Trust', 'Old Kent Financial', 'PND Financial Services', 'SouthTrust', 'S')

```